\documentclass[psamsfonts]{amsart}

%-------Packages---------
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{mathtools}
\usepackage{amssymb,amsfonts,amsmath,amsthm}
\usepackage{enumerate}
\usepackage{mathrsfs}
\usepackage[english]{babel}
\usepackage{tikz}
\usepackage{tikz-cd}

%--------Theorem Environments--------
%theoremstyle{plain} --- default
\newtheorem{thm}{Theorem}[section]
\newtheorem{cor}[thm]{Corollary}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{conj}[thm]{Conjecture}
\newtheorem{quest}[thm]{Question}

\theoremstyle{definition}
\newtheorem{defn}[thm]{Definition}
\newtheorem{defns}[thm]{Definitions}
\newtheorem{con}[thm]{Construction}
\newtheorem{exmp}[thm]{Example}
\newtheorem{exmps}[thm]{Examples}
\newtheorem{notn}[thm]{Notation}
\newtheorem{notns}[thm]{Notations}
\newtheorem{addm}[thm]{Addendum}
\newtheorem{exer}[thm]{Exercise}

\theoremstyle{remark}
\newtheorem{rem}[thm]{Remark}
\newtheorem{rems}[thm]{Remarks}
\newtheorem{warn}[thm]{Warning}
\newtheorem{sch}[thm]{Scholium}

\makeatletter
\let\c@equation\c@thm
\makeatother
\numberwithin{equation}{section}

\bibliographystyle{plain}

%------- Math definitions -----------
\input{defs}

%--------Meta Data: Fill in your info------
\title{Number Fields: An Introduction to Algebraic Number Theory}

\author{Pol Gómez Riquelme}

\date{Summer of 2018, June-August.}

\begin{document}

\begin{abstract}

This paper is a first introduction to number theory from a modern perspective, through algebraic methods. We review the necessary algebra to understand later material, present the usual setup of number fields, and develop the basic theory of unique factorization of Dedekind domains, prove the finiteness of the class number, and study the structure of the group of units of a given number field.

\end{abstract}

\maketitle

\tableofcontents

\section*{Introduction}

This paper is an attempt at a first introduction to number theory through a somewhat modern lens. With algebra as the fundamental language through which number theory is studied, the ``contemporary'' approach (insofar as ``classical'' number theory consists of essentially ad-hoc methods with little or no underlying framework) can seem daunting because of the machinery required: we aim at providing a survey of the first seven chapters of Jürgen Neukirch's popular \emph{Algebraic Number Theory}, with added background and slightly more prosaic motivations to fundamental concepts, the importance of which can only be fully grasped in retrospective.

The first chapter is a quick review of basic vocabulary in algebra. The second introduces the premise of algebraic number theory: a setup in terms of field theory, with heavy usage of the language of modules. The chapter contains fundamental discussion on integrality, and the classification theorem of finitely generated modules over the integral closure of some number field extension. While undeniably a mouthful, it is our hope that this paper will provide some intuition and the background necessary to make sense of the previous statement. The third chapter builds up towards two major results: it proves unique factorization in Dedekind domains (the natural setup of algebraic number theory), and presents the notion of the class group (which measures the ``expansion'' that has taken place by passing to Dedekind domains). The fourth chapter develops the theory of Minkowski to prove that the class group has finite cardinality (thus showing that this ``expansion'' is somehow controlled). Finally, the fifth and last chapter concludes with a structure theorem of the unit group of a number field (Dirichlet's unit theorem) -- and an application to the solutions of Pell's equation.

While necessarily limited in scope, we nevertheless hope that this paper provides an accessible survey to basic (and powerful) results in algebraic number theory.

\input{algebra}

\input{afields}

\input{ideals}

\input{lattices}

\input{mult}

\section*{Acknowledgments}
I am thankful to Owen Barrett for his guidance and patience during the entirety of the REU program; all the beautiful things in number theory that have been the subject of this paper would still be inaccessible to me without his many hours of help. Many thanks to Peter May for his unrelenting efforts at organizing this fantastic program.

\begin{thebibliography}{9}

\bibitem{lang}
S. Lang.
\emph{Algebra.}
Springer-Verlag. 2002.

\bibitem{neukirch}
J. Neukirch.
\emph{Algebraic Number Theory.}
Springer-Verlag. 1999.

\bibitem{rouseball}
W. W. Rouse Ball.
\emph{A Short Account of the History of Mathematics.}
Dover Publications. 1960.

\end{thebibliography}

\end{document}


